Galois characterization of function fields of \\ transcendence degree $1$ over number fields

### 2016-04-29 Master Thesis/synopsis.tex
Copy of proof to 3.1

>>>>

\begin{proof}
Let $\ell_1,\ell_2$ be two different prime numbers different from $\operatorname{char} k(w)$ and let $E_0 = E(\mu_{\ell_1\ell_2})$. Then $E_0/E$, and also $E'_0/E'$, satisfies the condition of \ref{2.6} (ii). Thus there exists a unique henselian defectless valuation $w'_{E'}$ of $E'$, so $E'$ contains a henselization $K'_{w'}$ of $w'_{E'}|_{K'}$. By applying the same argument to $\sigma^{-1}$ we find that $E' = K'_{w'}$.

Let $F$ be another henselization of $w$. Then $E, F$ are $K$-isomorphic, hence $E',F'$ are $K'$-isomorphic and the corresponding henselian valuations of $E', F'$ respectively are mapped to each other.
\end{proof}
